Tropical Andes plant occurrence data GBIF

### 2023-07-18 code/L0/L0_TropicalAndes_plants_TRY_traits.Rmd
update input file path add summary info to parallel occurrence

# Load required packages
```{r}

```

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php 
```{r}
try_data <- rtry_import("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY/23650_24112022083128/23650.txt", encoding = "Latin-1")
try_data <- as.data.frame(try_data)
```

```{r}

```

>>>>

# Load required packages
```{r}
library(rtry)
```

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php 
```{r}
try_data <- read.delim("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY/25496_17032023010024/25496.txt")
```

# Summary 
```{r}
glimpse(try_data)
```

```{r}
print("The number of records is")
nrow(try_data)
print("The number of species is" )
length(unique(try_data$species))
print("The number of families is" )
length(unique(try_data$family))
```
